My title

### 2024-09-26 outputs/paper/paper.qmd
cleaned up paper, and removed pie chart

@@

```{r ave-delay-streetcar}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Average Amount of Delay Time for Streetcars, by Incident Type
#| fig-align: center
streetcar_bar_chart <- create_bar_chart("Streetcar")
streetcar_bar_chart
```

```{r ave-delay-subway}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Average Amount of Delay Time for Subways, by Incident Type
#| fig-align: center

@@

@@

```{r delay-over-time}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Delay Time from 2014 to 2024
#| fig-align: center

>>>>

```{r total-delay-incident}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Average Amount of Delay Time for Buses by, Incident Type
#| fig-align: center

# Step 1: Calculate total delay time for each incident type
data_incident_total_delay <- data %>%
  group_by(Incident) %>%
  summarise(total_delay = sum(Delay, na.rm = TRUE), .groups = 'drop') %>%
  mutate(Incident = fct_reorder(Incident, total_delay, .desc = TRUE))  # Reorder by total_delay

# Step 2: Create the bar chart for total delay time by incident type
ggplot(data_incident_total_delay, aes(x = Incident, y = total_delay)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Total Delay Time by Incident Type", 
       x = "Incident Type", y = "Total Delay Time (Minutes)") +
  scale_y_continuous(labels = comma) +  # Format y-axis labels to be whole numbers with commas
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10))

@@

```{r ave-delay-streetcar}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Average Amount of Delay Time for Streetcars, by Incident Type
#| fig-align: center
streetcar_bar_chart <- create_bar_chart("Streetcar")
streetcar_bar_chart
```
```{r ave-delay-subway}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Average Amount of Delay Time for Subways, by Incident Type
#| fig-align: center

@@

```
```{r total-delay-time}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Total Delay Time from 2014 to 2024
#| fig-align: center
# Step 1: Convert the Date column to Date format (if it's not already) and group by month and vehicle type
data_total_delay_time <- data %>%
  mutate(Date = as.Date(Date)) %>%  # Ensure Date is in Date format
  group_by(month = floor_date(Date, "month"), vehicle) %>%  # Group by month and vehicle type
  summarise(total_delay = sum(Delay, na.rm = TRUE), .groups = 'drop')  # Summarize total delay

# Step 2: Create the line chart with 3 lines for each mode of transport
ggplot(data_total_delay_time, aes(x = month, y = total_delay, color = vehicle, group = vehicle)) +
  geom_line(size = 1) +  # Create the line chart with separate lines for each vehicle
  labs(title = "Total Incident Time by Mode of Transport (2014-2024)", 
       x = "Time", y = "Total Incident Time (Minutes)", color = "Vehicle Type") +
  theme_minimal() +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +  # Format the x-axis with yearly labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

@@

```{r delay-over-time}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Average Delay Time from 2014 to 2024
#| fig-align: center
